Paper TITLE

### 2016-08-05 code/Paper.Rmd
Modify alpha in map

ggplot(counts, aes(x = year, 
                   y = percent,
                   fill = fmtincrelpovcat)) + 
  geom_area(alpha = 0.9) +
  # Use a nice colour palette
  scale_fill_brewer(palette = "RdYlGn", 
                    # Reverse the order of legend items to match the
                    # stacking order
                    guide = guide_legend(reverse=TRUE)) +
  labs(title = "Amount of households relative to poverty line",
       x = "Year",
       y = "Precent of households",
       fill = "Household income
relative to poverty income") +
  theme_tufte()
```

>>>>

ggplot(counts, aes(x = year, 
                   y = percent,
                   fill = fmtincrelpovcat)) + 
  geom_area(alpha = 0.8) +
  # Use a nice colour palette
  scale_fill_brewer(palette = "RdYlGn", 
                    # Reverse the order of legend items to match the
                    # stacking order
                    guide = guide_legend(reverse=TRUE)) +
  labs(title = "Amount of households relative to poverty line",
       x = "Year",
       y = "Precent of households",
       fill = "Household income
relative to poverty income") +
  theme_tufte()
```
